\bf Cognitive control and semantic thought variability\\across sleep and wakefulness

### 2024-12-15 manuscript/manuscript.tex
replace experience sampling ref

% -----------------------------------------
% Modify page layout
% -----------------------------------------

@@

\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{authblk}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{newtxtext,newtxmath} % access Times New Roman
\usepackage{microtype} % prettifies typesetting and prevents some overfulls
\usepackage{parskip} % sets space between paragraphs
\usepackage{graphicx} % figures
\usepackage{booktabs} % tables
\usepackage[font=small,labelfont=bf,labelsep=period,singlelinecheck=false]{caption} % captions
\usepackage[backend=biber,style=nature,date=year,hyperref=false]{biblatex} % references
\addbibresource{references.bib}
% \usepackage{setspace} % to adjust line spacing
\usepackage[final,hyperfootnotes=false,hidelinks]{hyperref} % hyperlinks

@@

\par
We did not compare thought variability directly between waking and dreaming. The Dynamic Framework of Thought and other accounts make specific predictions about the relationship between waking and dreaming thought dynamics, but the large discrepancy between how our datasets were collected precluded deriving conclusive results from such an analysis. Dream reports in the current study were not collected immediately during or after they occurred, whereas waking reports were collected in real-time using experience sampling~\cite{trull2009}. Though dream reports are considered reliable accounts of experience~\cite{windt2013}, they are susceptible to memory fallacies~\cite{rosen2013}. Dream reports collected directly from REM awakenings differ substantially from morning reports, including a higher level of bizarreness~\cite{kirberg2022}. In this dataset, the longer gap between experience and reporting in the dream reports than the waking reports would have been a major confounding factor in any direct comparison between the two. Prior work using self-report measures of thought variability suggest that dreaming thought consists of similar levels of variability as task-independent waking thoughts, both of which show higher variability than task-dependent waking thoughts~\cite{gross2021}. Future work comparing waking and dreaming thoughts within-individuals using a serial-awakening paradigm~\cite{siclari2013} and language measures would provide valuable additional insights into the mechanisms of thought generation.

>>>>

@@

\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{authblk}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{newtxtext,newtxmath} % access Times New Roman
\usepackage{microtype} % prettifies typesetting and prevents some overfulls
\usepackage{parskip} % sets space between paragraphs
\usepackage{graphicx} % figures
\usepackage{booktabs} % tables
\usepackage[font=small,labelfont=bf,labelsep=period,singlelinecheck=false]{caption} % captions
\usepackage[backend=biber,style=nature,date=year,hyperref=false]{biblatex} % references
\usepackage[final,hyperfootnotes=false,hidelinks]{hyperref} % hyperlinks
\addbibresource{references.bib}

% -----------------------------------------
% Additional page formatting
% -----------------------------------------

@@

\par
We did not compare thought variability directly between waking and dreaming. The Dynamic Framework of Thought and other accounts make specific predictions about the relationship between waking and dreaming thought dynamics, but the large discrepancy between how our datasets were collected precluded deriving conclusive results from such an analysis. Dream reports in the current study were not collected immediately during or after they occurred, whereas waking reports were collected in real-time using experience sampling~\cite{shiffman2008}. Though dream reports are considered reliable accounts of experience~\cite{windt2013}, they are susceptible to memory fallacies~\cite{rosen2013}. Dream reports collected directly from REM awakenings differ substantially from morning reports, including a higher level of bizarreness~\cite{kirberg2022}. In this dataset, the longer gap between experience and reporting in the dream reports than the waking reports would have been a major confounding factor in any direct comparison between the two. Prior work using self-report measures of thought variability suggest that dreaming thought consists of similar levels of variability as task-independent waking thoughts, both of which show higher variability than task-dependent waking thoughts~\cite{gross2021}. Future work comparing waking and dreaming thoughts within-individuals using a serial-awakening paradigm~\cite{siclari2013} and language measures would provide valuable additional insights into the mechanisms of thought generation.
